---
title: "PairAssignment 02: Research Proposal"
authors: "Björn Boening, Laurence Hendry, Cody Koebnick"
date: "20. Oktober 2015"
output: ioslides_presentation
---

## Introduction: Research Question

My topic is about global anti-piracy measures. Thereof, my broad research question is: What is the influence of predictive models on piracy?

A yet provisionally, but more specific research question is: Do predictive models have a 
greater impact on anti-piracy measures when a hot spot for piracy can be identified (1), or do 
predictive models impact naval forces deployment (2)?

Piracy as an act of robbery or criminal violence against vessels is the key concept of my 
research project. The United Nations’ International Law Commission has described piracy 
not only happening at High Sea, but also in the air. My project focuses on maritime piracy, 
and thus only takes into account vessels on water. The International Chamber of 
Commerce’s International Maritime Bureau (IMB) has defined in 1992 piracy as “the act of 
boarding any vessel with an intent to commit theft or any other crime, and with an intent or 
capacity to use force in furtherance of that act”. The United Nations Convention on the Law 
of the Sea (1982) has defined piracy as “any illegal acts of violence, detention, or any act of 
depredation’ committed for private ends, in a ship-to-ship conflict that occurs in the high 
seas.”

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

